The problem and promise of scale in multilayer networks

### 2020-01-24 paper/manuscript.Rmd
edit movement ecol p1

In long-lived species, social phenotypes can change over their lifetimes in ways that can have affect fitness (Berger et al., 2015; Brent et al., 2017). These findings highlight the necessity to carefully consider the temporal scale that is meaningful for the proposed hypotheses, especially for understanding the relationship between an individuals social phenotypes and fitness. Further complicating the issue, social phenotypes can change over stages of ontogeny, although it is important to note that individuals progress through development at different rates (Tarka, Guenther, Niemelä, Nakagawa, & Noble, 2018). This variation can make defining appropriate temporal scales for testing the fitness implications of an individual’s social phenotype over different stages of ontogeny even more difficult. However, considering fine temporal scales may provide insight across development stages that may otherwise be missed (CITE-myself??). Multilayer networks provide a framework to test hypotheses linking social phenotypes and fitness across temporal scales. Because of the non-independent nature of social interactions and associations, especially over time, it is hard to test hypotheses about social dynamics with a suitable null control (Farine, 2017; Proskurnikov & Tempo, 2017). Using the framework of multilayer networks, making layers of different temporal periods provides a way to make appropriate null models to test questions about the dynamics of an individual’s social network position over multiple aggregated time periods.

@@

Animal movement undoubtedly affects the social environment (Strandburg-Peshkin et al. 2015) and multilayer networks are no exception (Mourier et al. 2019). Movement is a dynamic process and is related to an individual’s space use as well as the resources consumed within their home range (Van Moorter et al. 2016). Collective movement can reduce group-level predation via detection-dilution trade-offs, while it can also improve information transfer about the quality or location of resources (Jolles et al. 2019). Social processes, movement decisions, and space use are therefore inextricably linked.

>>>>

In long-lived species, social phenotypes can change over their lifetimes in ways that can affect fitness (Berger et al., 2015; Brent et al., 2017). These findings highlight the necessity to carefully consider the temporal scale that is meaningful for the proposed hypotheses, especially for understanding the relationship between an individuals social phenotypes and fitness. Further complicating the issue, social phenotypes can change over stages of ontogeny, although it is important to note that individuals progress through development at different rates (Tarka, Guenther, Niemelä, Nakagawa, & Noble, 2018). This variation can make defining appropriate temporal scales for testing the fitness implications of an individual’s social phenotype over different stages of ontogeny even more difficult. However, considering fine temporal scales may provide insight across development stages that may otherwise be missed (CITE-myself??). Multilayer networks provide a framework to test hypotheses linking social phenotypes and fitness across temporal scales. Because of the non-independent nature of social interactions and associations, especially over time, it is hard to test hypotheses about social dynamics with a suitable null control (Farine, 2017; Proskurnikov & Tempo, 2017). Using the framework of multilayer networks, making layers of different temporal periods provides a way to make appropriate null models to test questions about the dynamics of an individual’s social network position over multiple aggregated time periods.

@@

Animal movement undoubtedly affects the social environment (Strandburg-Peshkin et al. 2015), and multilayer networks are no exception (Mourier et al. 2019). Movement is a dynamic process that is related to the resources an individual consumes within their home range and their general space use (Van Moorter et al. 2016). Collective movement can reduce group-level predation via detection-dilution trade-offs and improve information transfer about the quality or location of resources to other group members (Jolles et al. 2019). Social processes, movement decisions, and space use are therefore inextricably linked.
